Peering Through Censorship:\\Tackling Internet Censorship Using P2P Networking

### 2023-02-07 paper.tex
Spelling

% File 'gusample.tex' -- Mark Maloof, Michael A. Covington, Isidor Ruderfer
% (Revised 15 December 2010)
% This is an example of how to format a thesis or dissertation using LaTeX 2e
% with 'guthesis.sty' VERSION 3.4 OR LATER.

@@

% If there are any other \usepackage commands, put them here.

@@

\newtheorem{theorem}{Theorem}[section]
\newtheorem*{adversary}{Adversary}
\newenvironment{proof}[0]{\textit{Proof.}}{}
\newcommand{\qed}{\hfill $\Box$}

@@

\professor{Micah Sherr}
%\secondprofessor{Alonzo Church}   % Only if you have 2 major professors!

@@

\memberi{Lisa Singh}
\memberii{Benjamin Ujcich}
% Use \memberiii, \memberiv, \memberv for up to 3 more members if needed.

@@

People us the internet to communicate and share a variety of content. Some entities choose to censor internet connections. These entities may range from individual network administrators to a full nation-state. In this paper, we explore the state of censorship, existing circumvention sytems, and we design and build a system which tackles several of the limitations present in state of the art systems. [LATER: Add xrefs to sections]

@@

We also provide an overview of the state of peer to peer (P2P) networking, focusing on succesful project operating in the real world. We provide a deeper dive into the Interplanetary File System (IPFS) and the underlying networking library, LibP2P. These programs are used extensively in out proposed system.

@@

The term censorship has taken on a life of it's own in the modern social and political context. We are \emph{not} exploring the general connotation of censorship, rather, we are exploring a specific type of censorship that existing in a networking (particularly internetworking) context. We will explore some key concepts and present a short model of networking.

@@

\begin{itemize}
  \item Internet Protocol (IP) addresses: These are used to represent endpoints of a connection, and are used for routing. Within a network, other identifiers, such as MAC addresses, are used for routing, however, we are focused on routing between networks and will only consider IP based routing as we explore censorship circumvention. We will use IPv4 addresses throughout as sample addresses, though conceptually IPv6 addresses function similarly for the focuses of this paper.
  \item Domain Name System (DNS): DNS resolution is used to map from human-readable and memorizable addresses that map to IP addresses (e.g. georgetown.edu resolved to 23.185.0.2 at the time of writing). [TODO: Explore the transparency of these, DNSSEC, etc]
  \item Router: Routers perform routing for networking, as well as other functions that act on network traffic. They may be the home of a NAT, a firewall, or censorship software. The controller of a router may access and manipulate any traffic which passes through it.
  \item Firewalls: These are software that may restrict traffic based on rules. These rules may be simple or complex. These have positive uses, such as securing a network from attacks.
  \item Network address translation (NAT): A NAT is used to map network addresses seen on one side of a router to those seen on the other side of a router. These are frequently used to house potentially thousands of devices behind a single internet facing IP address. Most humans use devices located behind a NAT.
\end{itemize}

@@

We recognize that some users run heinous services on the web - most of which are illegal in any existing jurisdiction. We believe that the best approach for ceasing access to these heinous services is best done through a legal system - ie, investigating and identifying the perpetrator(s), turning off the service directly, and prosecuting any perpetrator(s) of said acts. We note that most morally reprehensible acts that are frequently associated with anonymity and censorship circumvention systems involve actions that occur in the real world (e.g. exploitation of children, weapon/drug/human trafficking all involve actions that occur in the real world either prior to distribution on the internet or triggered by actions on the internet).

The only notable class of crime which can occur without physical, real-world actions is piracy/IP violations. We believe that targetted legal actions (e.g. DMCA takedowns) can mitigate the issue, and that the cost of further mitigation through censorship would lead to large collateral damage of legal content and a chilling effect of legal speech and usage of the web, and as such the possibility of a circumvention system being used for piracy/IP violations is an acceptable risk given the ability to mitigate damage through the legal system.

@@

An adversary has an \textbf{area of influence}. This is an area an adversary controls the network of, and can control (either directly or through compulsion) any service providers within. We assume an adversary may have an area of influcence consisting of several nations, with at least one nation outside of the area of influence of \emph{any} censor.\footnote{This does not mean that this nation does not have the technical capability to censor, but rather does not perform any censorship either directly or via threatening a start of censorship.}

@@

We also assume that our adversary only takes actions \textbf{on-the-wire} and at \textbf{service providers} within their area of influence - effectively, the adversary isn't interested in any individual in particular and is performing a dragnet operation, rather than an operation targetting a specific entity. We can use a thought experiment to justify this: if an adversary had a person looking over your shoulder or using video surveillance, they could simply look at what you are doing and punish you directly, no need to expend the resources needed to censor the web.

We assume our adversary has some interest in the utility of the internet and certain technologies on the internet. This means two things: an adversary will not shut down the internet in it's entirety\footnote{Internet shutdowns are a trivial way to censor forbidden internet usage - at the expense of shutting down any non-forbidden usage. [TODO: Discuss prior shut downs in another section and xref]} and an adversary has some threshold of unacceptable collateral damage caused by potential censorship techniques.\footnote{Similar to a full internet shutdown, if an adversary wanted to block all access to a specific HTTP site, they could block \emph{all} HTTP traffic, at the expense of blocking every HTTP site. This piecemeal web censorship could even be thwarted with a circumvention system that simply proxies HTTP traffic outside of the area of influence within an unblocked protocol and connects to HTTP sites from outside the area of influcence. This starts to show that any non-complete shutdown of internet traffic may have gaps for circumvention techniques. We discuss collateral damage further in [TODO: xref].}

@@

Censorship circumvention arose as a by-product of tools made for purposes that were not focused on censorship circumvention. As primitive censorship began, people realized that anonymity software such as Tor or even a basic proxy could be used to access services that would otherwise be blocked. The entrances to these proxy services and Tor were accessed via well known IP addresses or DNS names.\footnote{The reason these were well known is that, if you want the public to access your service, they must know how to access these services, including the addresses of your service. These must be made public to allow people to access your service. A censor has access to public information.} Censors began being blocking access to these services, in additon to their original censorship targets. This set off a "censorship arms race."

At this point, those who used and built the anonymity software recognized that censorship circumvention would be crucial for maintaining access to these tools, and others realized that censorship circumvention in-and-of itself would be useful. This effectively led to the rise of a subdiscipline that draws heavily from networking, security, and even game theory, but also exists independently from those subdisciplines, with a variety of stakeholders including governments, NGOs, non-profits, independent programmers, academics, and others interested in developing censorship circumvention techniques. This also leads to a relatively unique feature of this discipline - some techniques were developped in academia, some techniques were developped in the real world, and some were developped in both, and ignoring the results from either thread of research and observation can lead to the development of flawed systems.

@@

The bedrock of the theory underlying succesful provision of access to proxies is collateral damage.

@@

We begin with a basic model - an adversary will engage in the censorship of service $x$ if $B_x - C_x > 0$, where $B_x$ is the average benefit per user of engaging in censorship of service $x$ and $C_x$ is the average cost of engaging in censorship of service $x$. We will refine this formula by switching to a focus on censorship techniques - $(b_{x,1} + b_{x,2} + ... + b_{x,n}) - C_x > 0$, where $b_{x,n}$ is the average benefit per user of censoring service $n$ using method $x$. A censor will engage in any censorhip method where the average benefit reaped by censoring \emph{any} desired services using that method is greater than the cost. Also note that these benefits and costs are based on how they are \emph{perceived} by the censor, not by an objective, bird-eye view of good vs. bad, and they may account for a variety of benefits/cost, including direct financial costs, but also including less tangible value such as "stability".

@@

We will now break down cost further. $C_x = f_x + m_x$ - where $f_x$ is the fixed cost per user of setting up method $x$ and $m_x$ is the marginal cost of actively engaging in $x$ per user. We will drop $f_x$ from further consideration (ie, $C_x = m_x$) - the cost of setting up a method is a one time cost, and to an adversary with unlimited resources, expending a one time cost averages to $0$ over the long run. We will now explore the marginal cost of $x$. Censorship tools may slow down "good" traffic, and they may erroneously block access to good services. Therefore, $C_x = s_x*i_x + (u_{x,1}*c_{x,1} + u_{x,2}*c_{x,2} + ...  + u_{x,n}*c_{x,n})$, where $c_{x,n}$ is the average cost of blocking service $n$ per user, $u_{x,n}$ is the same as above, $s_x$ is the average fraction of the total value of unblocked traffic retained (due to the reduction in speed caused by enabling method $x$),\footnote{Note that an adversary may engage in multiple stages of filtering, so some subsets of unblocked traffic may experience no slowdown, while some might experience more. For the purposes of our analysis, we can use the average across all allowed traffic.}, and $i_x$ is the value per user of access to all unblocked sites. Combining the above, we see
$(u_{x,1}*b_{x,1} + u_{x,1}*b_{x,2} + ... + u_{x,n}*b_{x,n}) - s_x*i_x + (c_{x,1} + c_{x,2} + ...  + c_{x,n}) > 0$, or, more sucintly:
\begin{equation}
-s_x*i_x + \sum_{s=1}^{n}u_{x,s}*v_{x,s} > 0
\end{equation}
where $v_{x,s} = b_{x,s} - c_{x,s}$.

We could conclude here if a censor engaged in censorship solely using a singular method of censorship - however, censors engage in multiple methods of censorship, and the benefit of succesfully blocking a site is not distributed multiple times if it's blocked by multiple methods, the benefit is only achieved based on new users blocked by a method, or, in short, a singular censorship system $x$ will be implemented if:
\begin{equation}
-s_x*i_x + \sum_{s=1}^{n}\Delta u_{x,s}*v_{x,s} > 0
\end{equation}
Note that all variables are the same, except $i_x$ is now the value per user of access to all unblocked sites prior to enabling censorship system $x$ and $\Delta u_{x,s}$ is the change in the fraction of users who can access service $s$ after enabling $x$.

We have now established an equation used to determine if a censor will enable an individual system, taking existing sytems (or lack thereof) as a given. This is not reflective of reality, where a rational censor will evaluate \emph{all} of their active and potentical circumvention systems in conjunction.

@@

\subsection{Real world vs. academic theory}

@@

Additionally, usability is also a crucial issue [TODO: COVER THIS IN RELATED WORK], and we identify two crucial issues where at least one of these affects every previously discussed system:
\begin{itemize}
  \item Low bandwidth/poor performance: Users want a good experience on the web. Some of these methods are completely unusable for proxying the entirety of a web session. Additionally, many of these items are tied to usage of Tor. While we support usage of Tor, it slows down web browsing even without circumvention tools in use, and usage can [result in broken behavior on some websites/some sites block Tor TODO: explore and cite either in fn or related work].
  \item Barriers to entry: Every system we've explored that are usable by a layperson require usage in conjunction with Tor - and a layperson must be aware Tor exists, not be biased against it,\footnote{Some individuals believe that Tor is only used by criminals, and while we do not believe this is true, dispelling misinformation at a large scale is a herculean task that we will assume is not accomplishable in the short and medium term [TODO: Citing this would be good]} know how to get it, and not be censored when getting it.\footnote{Acquiring Tor is frequently censored for users, which means that a user \emph{must} acquire it prior to being under a censorship regime, or must have some out of band channel for acquisition. [TODO: Worth citing, may be worth bumping up importance]}
\end{itemize}

Below, we propose a system with a clear theoretical backing and acheivable goals based on both theory and real-world observations. [TODO: xref] We also address these other key issues.

@@

We are \emph{not} aiming to provide anonymity.\footnote{Perhaps our system could be used to access an anonymity system, but we do not want to guarentee anonymity or guarentee that the system will not leak information that may break anonymity, though we are not delibrately trying to break anonymity, we are also not evaluating our system for it at this point.} We feel the need to emphasize this, as most current systems that are functional in the real world are used purely as a PT by Tor.\footnote{Our system could be used as a PT, as we do have a golang implementation, however, evaluating this system for usage as a PT is reserved for future work. [TODO: XREF PTs]}

@@

Earlier, [TODO: xref] we discussed a variety of censorship circumvention systems. Observing how and why each of these work, and the drawbacks associated with each of them will allow us to formulate goals we wish to acheive, working techniques we may use, and a theory for our systems function. We present a short summary of previous systems in [TODO: xref table], comparing and contrasting their succesful techniques and transports, and their individual drawbacks.

@@

We first note that systems with deployment difficulty (refraction networking) as their primary limitation rely on either a single or handful of \emph{large}, \emph{continuously cooperative} entities (all very large tech corporations). This makes the circumvention method brittle - ie, a change of heart of very few entities could negate the effectiveness of this method. We believe that not only is this a possibility, but it is a \emph{likely} possibility - we note that adversaries may be as large as a collective of nations in our model - and given the profit maximization of corporations, these entitites will want to perform business in the sphere of influence of our adversary. The adversary could pressure the entity to shut down the system in order to perform business within, with, and with citizens of the sphere of influence of the adversary. Economic theory implies that this will occur in the long run. [TODO: shore this up with both more clear wording and with some cites to examples] Due to this limitation we will not be building on refraction networking for our system.

@@

We are left with systems whose primary limitation is scalability. We see that Snowflake is the only remaining existing system. Snowflake was developped primarily in the real world - and we know it works in the real world - but to build off of this success we want to formalize that success and that system design.

@@

We propose a theoretical censorship system, $s_{new}$. We will consider $S \cup {s_{new}}$. Our censor will reevaluate the utility of their system using every permutation of this larger set. This means that they will evaluate adding $s_{new}$ to their system, and keeping all existing systems or removing some of them and adding this new one. We will let this new set be $S_{new}$. We have two potential cases:
\begin{itemize}
  \item $S_{new}$ does not include $s_{new}$ - ie, $S_{new} = S$. In this case, the censor is not engaging any new censorship sytems.
  \item $S_{new}$ includes $s_{new}$ - ie, they engaged the new system. In this case we will assume that they will never disable an old system. [TODO: Can we prove that they will never disable an old system?] This means we can evaluate a new system using a simplified formula from earlier:
  \begin{equation}
-s_x*i_x + \sum_{s=1}^{n}\Delta u_{x,s}*v_{x,s} > 0
  \end{equation}
  [TODO: XXX: FIX S REUSE IN FORMULAS]
\end{itemize}

@@

>>>>

@@

% If there are any other \usepackage commands, put them here.
\usepackage{amsthm}

@@

\newtheorem{theorem}{Theorem}[section]
\newtheorem{adversary}{Adversary Model}

@@

\professor{Micah Sherr}

@@

\memberi{Lisa Singh}
\memberii{Benjamin Ujcich}

@@

People us the internet to communicate and share a variety of content. Some entities choose to censor internet connections. These entities may range from individual network administrators to a full nation-state. In this paper, we explore the state of censorship, existing circumvention systems, and we design and build a system which tackles several of the limitations present in state of the art systems. [LATER: Add xrefs to sections]

@@

We also provide an overview of the state of peer to peer (P2P) networking, focusing on successful project operating in the real world. We provide a deeper dive into the Interplanetary File System (IPFS) and the underlying networking library, LibP2P. These programs are used extensively in out proposed system.

@@

The term censorship has taken on a life of it's own in the modern social and political context. We are \emph{not} exploring the general connotation of censorship, rather, we are exploring a specific type of censorship that existing in a networking (particularly inter-networking) context. We will explore some key concepts and present a short model of networking.

@@

\begin{itemize}
  \item Internet Protocol (IP) addresses: These are used to represent endpoints of a connection, and are used for routing. Within a network, other identifiers, such as MAC addresses, are used for routing, however, we are focused on routing between networks and will only consider IP based routing as we explore censorship circumvention. We will use IPv4 addresses throughout as sample addresses, though conceptually IPv6 addresses function similarly for the focuses of this paper.
  \item Domain Name System (DNS): DNS resolution is used to map from human-readable and memorable addresses that map to IP addresses (e.g. georgetown.edu resolved to 23.185.0.2 at the time of writing). [TODO: Explore the transparency of these, DNSSEC, etc]
  \item Router: Routers perform routing for networking, as well as other functions that act on network traffic. They may be the home of a NAT, a firewall, or censorship software. The controller of a router may access and manipulate any traffic which passes through it.
  \item Firewalls: These are software that may restrict traffic based on rules. These rules may be simple or complex. These have positive uses, such as securing a network from attacks.
  \item Network address translation (NAT): A NAT is used to map network addresses seen on one side of a router to those seen on the other side of a router. These are frequently used to house potentially thousands of devices behind a single internet facing IP address. Most humans use devices located behind a NAT.
\end{itemize}

@@

We recognize that some users run heinous services on the web - most of which are illegal in any existing jurisdiction. We believe that the best approach for ceasing access to these heinous services is best done through a legal system - IE, investigating and identifying the perpetrator(s), turning off the service directly, and prosecuting any perpetrator(s) of said acts. We note that most morally reprehensible acts that are frequently associated with anonymity and censorship circumvention systems involve actions that occur in the real world (e.g. exploitation of children, weapon/drug/human trafficking all involve actions that occur in the real world either prior to distribution on the internet or triggered by actions on the internet).

The only notable class of crime which can occur without physical, real-world actions is piracy/IP violations. We believe that targeted legal actions (e.g. DMCA take-downs) can mitigate the issue, and that the cost of further mitigation through censorship would lead to large collateral damage of legal content and a chilling effect of legal speech and usage of the web, and as such the possibility of a circumvention system being used for piracy/IP violations is an acceptable risk given the ability to mitigate damage through the legal system.

@@

An adversary has an \textbf{area of influence}. This is an area an adversary controls the network of, and can control (either directly or through compulsion) any service providers within. We assume an adversary may have an area of influence consisting of several nations, with at least one nation outside of the area of influence of \emph{any} censor.\footnote{This does not mean that this nation does not have the technical capability to censor, but rather does not perform any censorship either directly or via threatening a start of censorship.}

@@

We also assume that our adversary only takes actions \textbf{on-the-wire} and at \textbf{service providers} within their area of influence - effectively, the adversary isn't interested in any individual in particular and is performing a dragnet operation, rather than an operation targeting a specific entity. We can use a thought experiment to justify this: if an adversary had a person looking over your shoulder or using video surveillance, they could simply look at what you are doing and punish you directly, no need to expend the resources needed to censor the web.

We assume our adversary has some interest in the utility of the internet and certain technologies on the internet. This means two things: an adversary will not shut down the internet in it's entirety\footnote{Internet shutdowns are a trivial way to censor forbidden internet usage - at the expense of shutting down any non-forbidden usage. [TODO: Discuss prior shut downs in another section and xref]} and an adversary has some threshold of unacceptable collateral damage caused by potential censorship techniques.\footnote{Similar to a full internet shutdown, if an adversary wanted to block all access to a specific HTTP site, they could block \emph{all} HTTP traffic, at the expense of blocking every HTTP site. This piecemeal web censorship could even be thwarted with a circumvention system that simply proxies HTTP traffic outside of the area of influence within an unblocked protocol and connects to HTTP sites from outside the area of influence. This starts to show that any non-complete shutdown of internet traffic may have gaps for circumvention techniques. We discuss collateral damage further in [TODO: xref].}

@@

Censorship circumvention arose as a by-product of tools made for purposes that were not focused on censorship circumvention. As primitive censorship began, people realized that anonymity software such as Tor or even a basic proxy could be used to access services that would otherwise be blocked. The entrances to these proxy services and Tor were accessed via well known IP addresses or DNS names.\footnote{The reason these were well known is that, if you want the public to access your service, they must know how to access these services, including the addresses of your service. These must be made public to allow people to access your service. A censor has access to public information.} Censors began being blocking access to these services, in addition to their original censorship targets. This set off a "censorship arms race."

At this point, those who used and built the anonymity software recognized that censorship circumvention would be crucial for maintaining access to these tools, and others realized that censorship circumvention in-and-of itself would be useful. This effectively led to the rise of a subdiscipline that draws heavily from networking, security, and even game theory, but also exists independently from those subdisciplines, with a variety of stakeholders including governments, NGOs, non-profits, independent programmers, academics, and others interested in developing censorship circumvention techniques. This also leads to a relatively unique feature of this discipline - some techniques were developed in academia, some techniques were developed in the real world, and some were developed in both, and ignoring the results from either thread of research and observation can lead to the development of flawed systems.

@@

The bedrock of the theory underlying successful provision of access to proxies is collateral damage.

@@

We begin with a basic model - an adversary will engage in the censorship of service $x$ if $B_x - C_x > 0$, where $B_x$ is the average benefit per user of engaging in censorship of service $x$ and $C_x$ is the average cost of engaging in censorship of service $x$. We will refine this formula by switching to a focus on censorship techniques - $(b_{x,1} + b_{x,2} + ... + b_{x,n}) - C_x > 0$, where $b_{x,n}$ is the average benefit per user of censoring service $n$ using method $x$. A censor will engage in any censorship method where the average benefit reaped by censoring \emph{any} desired services using that method is greater than the cost. Also note that these benefits and costs are based on how they are \emph{perceived} by the censor, not by an objective, bird-eye view of good and bad, and they may account for a variety of benefits/cost, including direct financial costs, but also including less tangible value such as "stability".

@@

We will now break down cost further. $C_x = f_x + m_x$ - where $f_x$ is the fixed cost per user of setting up method $x$ and $m_x$ is the marginal cost of actively engaging in $x$ per user. We will drop $f_x$ from further consideration (IE, $C_x = m_x$) - the cost of setting up a method is a one time cost, and to an adversary with unlimited resources, expending a one time cost averages to $0$ over the long run. We will now explore the marginal cost of $x$. Censorship tools may slow down "good" traffic, and they may erroneously block access to good services. Therefore, $C_x = s_x*i_x + (u_{x,1}*c_{x,1} + u_{x,2}*c_{x,2} + ...  + u_{x,n}*c_{x,n})$, where $c_{x,n}$ is the average cost of blocking service $n$ per user, $u_{x,n}$ is the same as above, $s_x$ is the average fraction of the total value of unblocked traffic retained (due to the reduction in speed caused by enabling method $x$),\footnote{Note that an adversary may engage in multiple stages of filtering, so some subsets of unblocked traffic may experience no slowdown, while some might experience more. For the purposes of our analysis, we can use the average across all allowed traffic.}, and $i_x$ is the value per user of access to all unblocked sites. Combining the above, we see
$(u_{x,1}*b_{x,1} + u_{x,1}*b_{x,2} + ... + u_{x,n}*b_{x,n}) - s_x*i_x + (c_{x,1} + c_{x,2} + ...  + c_{x,n}) > 0$, or, more succinctly:
\begin{equation}
-s_x*i_x + \sum_{s=1}^{n}u_{x,s}*v_{x,s} > 0
\end{equation}
where $v_{x,s} = b_{x,s} - c_{x,s}$.

We could conclude here if a censor engaged in censorship solely using a singular method of censorship - however, censors engage in multiple methods of censorship, and the benefit of successfully blocking a site is not distributed multiple times if it's blocked by multiple methods, the benefit is only achieved based on new users blocked by a method, or, in short, a singular censorship system $x$ will be implemented if:
\begin{equation}
-s_x*i_x + \sum_{s=1}^{n}\Delta u_{x,s}*v_{x,s} > 0
\end{equation}
Note that all variables are the same, except $i_x$ is now the value per user of access to all unblocked sites prior to enabling censorship system $x$ and $\Delta u_{x,s}$ is the change in the fraction of users who can access service $s$ after enabling $x$.

We have now established an equation used to determine if a censor will enable an individual system, taking existing systems (or lack thereof) as a given. This is not reflective of reality, where a rational censor will evaluate \emph{all} of their active and potential circumvention systems in conjunction.

@@

\subsection{Real world and academic theory}

@@

Additionally, usability is also a crucial issue [TODO: COVER THIS IN RELATED WORK], and we identify two crucial issues where at least one of these affects every previously discussed system:
\begin{itemize}
  \item Low bandwidth/poor performance: Users want a good experience on the web. Some of these methods are completely unusable for proxying the entirety of a web session. Additionally, many of these items are tied to usage of Tor. While we support usage of Tor, it slows down web browsing even without circumvention tools in use, and usage can [result in broken behavior on some websites/some sites block Tor TODO: explore and cite either in fn or related work].
  \item Barriers to entry: Every system we've explored that are usable by a layperson require usage in conjunction with Tor - and a layperson must be aware Tor exists, not be biased against it,\footnote{Some individuals believe that Tor is only used by criminals, and while we do not believe this is true, dispelling misinformation at a large scale is a herculean task that we will assume is not possible in the short and medium term [TODO: Citing this would be good]} know how to get it, and not be censored when getting it.\footnote{Acquiring Tor is frequently censored for users, which means that a user \emph{must} acquire it prior to being under a censorship regime, or must have some out of band channel for acquisition. [TODO: Worth citing, may be worth bumping up importance]}
\end{itemize}

Below, we propose a system with a clear theoretical backing and achievable goals based on both theory and real-world observations. [TODO: xref] We also address these other key issues.

@@

We are \emph{not} aiming to provide anonymity.\footnote{Perhaps our system could be used to access an anonymity system, but we do not want to guarantee anonymity or guarantee that the system will not leak information that may break anonymity, though we are not deliberately trying to break anonymity, we are also not evaluating our system for it at this point.} We feel the need to emphasize this, as most current systems that are functional in the real world are used purely as a PT by Tor.\footnote{Our system could be used as a PT, as we do have a Golang implementation, however, evaluating this system for usage as a PT is reserved for future work. [TODO: XREF PTs]}

@@

Earlier, [TODO: xref] we discussed a variety of censorship circumvention systems. Observing how and why each of these work, and the drawbacks associated with each of them will allow us to formulate goals we wish to achieve, working techniques we may use, and a theory for our systems function. We present a short summary of previous systems in [TODO: xref table], comparing and contrasting their successful techniques and transports, and their individual drawbacks.

@@

We first note that systems with deployment difficulty (refraction networking) as their primary limitation rely on either a single or handful of \emph{large}, \emph{continuously cooperative} entities (all very large tech corporations). This makes the circumvention method brittle - IE, a change of heart of very few entities could negate the effectiveness of this method. We believe that not only is this a possibility, but it is a \emph{likely} possibility - we note that adversaries may be as large as a collective of nations in our model - and given the profit maximization of corporations, these entities will want to perform business in the sphere of influence of our adversary. The adversary could pressure the entity to shut down the system in order to perform business within, with, and with citizens of the sphere of influence of the adversary. Economic theory implies that this will occur in the long run. [TODO: shore this up with both more clear wording and with some cites to examples] Due to this limitation we will not be building on refraction networking for our system.

@@

We are left with systems whose primary limitation is scalability. We see that Snowflake is the only remaining existing system. Snowflake was developed primarily in the real world - and we know it works in the real world - but to build off of this success we want to formalize that success and that system design.

@@

We propose a theoretical censorship system, $s_{new}$. We will consider $S \cup {s_{new}}$. Our censor will reevaluate the utility of their system using every permutation of this larger set. This means that they will evaluate adding $s_{new}$ to their system, and keeping all existing systems or removing some of them and adding this new one. We will let this new set be $S_{new}$. We have two potential cases:
\begin{itemize}
  \item $S_{new}$ does not include $s_{new}$ - IE, $S_{new} = S$. In this case, the censor is not engaging any new censorship systems.
  \item $S_{new}$ includes $s_{new}$ - IE, they engaged the new system. In this case we will assume that they will never disable an old system. [TODO: Can we prove that they will never disable an old system?] This means we can evaluate a new system using a simplified formula from earlier:
  \begin{equation}
-s_x*i_x + \sum_{s=1}^{n}\Delta u_{x,s}*v_{x,s} > 0
  \end{equation}
  [TODO: XXX: FIX S REUSE IN FORMULAS]
\end{itemize}

@@

[TODO: Cite raven email study]
